---
title: "**Male _CS_ courtship behaviour when paired with female aDN>TNT**"
author: "Aaron M. Allen"
date: "5th December 2020"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    theme: readable
    df_print: paged
    fig_width: 8.5
    fig_height: 5
---


```{r setup, echo = FALSE, cache = FALSE}
knitr::opts_chunk$set(dev = c('png', 'cairo_pdf'), 
                      fig.align = 'center', fig.height = 5, fig.width = 8.5, 
                      pdf.options(encoding = "ISOLatin9.enc"),
                      fig.path='figures/', warning=FALSE, message=FALSE)

#options(width = 120)
```


# **Load packages**

Loading in the packages that we'll need for the analysis.

```{r}
library(tidyverse)
library(survminer)
library(survival)
library(data.table)
library(ggpubr)
library(zoo)
library(ggbeeswarm)
library(cowplot)
```

# **Load data**

This first bit is a lot of data import and manipulation to get it already to plot the courtship features.



First we'll load in the "key" tables with the genotypes, and do a little cleaning.

```{r message=FALSE}
genotypes <- read_csv("female_adn_ids.csv",col_names = TRUE)
head(genotypes)
```


One pair of flies didnt' copulate after one hour.

```{r}
sum(is.na(genotypes$copulation_time))
```

Copulation times were deduced from an mp4 video, which starts before the tracking and so needs to be offset.

```{r}
video_offset <- read_csv("video_offset.csv",col_names = TRUE)
head(video_offset)
```


```{r}
genotypes <- left_join(genotypes,video_offset)
genotypes <- genotypes %>% 
  mutate(mp4_cop_time=copulation_time,
        copulation_time=mp4_cop_time-offset)
head(genotypes)
```



One fly had already started to copulate by the time the tracking started.

```{r}
sum(genotypes$copulation_time<0,na.rm = T)
min(genotypes$copulation_time,na.rm = T)
genotypes$copulation_time[genotypes$copulation_time<0] <- 0
sum(genotypes$copulation_time<0,na.rm = T)
```




We also want to populate this table with the Id numbers for the matched females in each chamber. We are simply duplicating the `genotypes` table and if the male `fly_id` was odd, then we increment the female Id, and if the male `fly_id` was even then we decrement the Id. Finally we change the male genotype to "_CS_".

```{r}
genotypes <- genotypes %>% mutate(treatment = genotype)
female_genotypes <- genotypes
even_ids <- (genotypes$fly_id %% 2) == 0
odd_ids <- (genotypes$fly_id %% 2) != 0
female_genotypes$fly_id[even_ids] = female_genotypes$fly_id[even_ids] - 1
female_genotypes$fly_id[odd_ids] = female_genotypes$fly_id[odd_ids] + 1
genotypes$genotype <- "CS"
head(female_genotypes)
```



Now we merge the male and female `genotypes` tables.


```{r}
all_genotypes <- bind_rows(genotypes,female_genotypes)
all_genotypes <- all_genotypes %>% 
  unite("uni_fly",video,fly_id,remove = FALSE)
head(all_genotypes)
```




And now we can read in all the csv files with all the raw tracking and JAABA annotated behaviours.


```{r}
rawdata_list <- list.files("./",recursive = TRUE) %>% str_subset("_ALLDATA.csv")
all_rawdata <- tibble()
for (rawdata_file in rawdata_list) {
  temp <- fread(input = paste0("./",rawdata_file), showProgress = FALSE)
  all_rawdata <- bind_rows(all_rawdata,temp)
}
head(all_rawdata)
```





Define a few functions to compute the relative x and y postions of each fly in each chamber.

```{r}
# calculates relative y value based on data from feat.mat
calculate_yrel <- function(theta,dist){
  yrel=dist*cos(theta)
  return(yrel)
}
calculate_xrel <- function(ori,xmale,xfemale,yrel,ppm=14.85){
  xmale_mm=xmale/ppm
  xfemale_mm=xfemale/ppm
  xrel = (xfemale_mm - (cos(ori)*yrel+xmale_mm))/(sin(ori))
  return(xrel)
} 
calculate_xrel_abs <- function(theta,dist){
  xrel=dist*sin(theta)
  return(xrel)
}
```




And calculate those relative x and y positions.


```{r}
all_rawdata <- all_rawdata %>% 
  arrange(FileName,Arena,Frame)

all_rawdata$rel_y_other <- NA
all_rawdata$rel_x_other <- NA
all_rawdata$rel_x_abs_other <- NA
all_rawdata$rel_x_abs_corr_other <- NA

all_rawdata$rel_y_other[seq(1,nrow(all_rawdata),2)] = calculate_yrel(all_rawdata$facing_angle__rad[seq(1,nrow(all_rawdata),2)],
                                                         all_rawdata$dist_to_other__mm[seq(1,nrow(all_rawdata),2)])

all_rawdata$rel_x_other[seq(1,nrow(all_rawdata),2)] = calculate_xrel(ori = all_rawdata$ori__rad[seq(1,nrow(all_rawdata),2)],
                                                         xmale = all_rawdata$pos_x__px[seq(1,nrow(all_rawdata),2)],
                                                         xfemale = all_rawdata$pos_x__px[seq(2,nrow(all_rawdata),2)],
                                                         yrel = calculate_yrel(all_rawdata$facing_angle__rad[seq(1,nrow(all_rawdata),2)],
                                                                               all_rawdata$dist_to_other__mm[seq(1,nrow(all_rawdata),2)]))

all_rawdata$rel_x_abs_other[seq(1,nrow(all_rawdata),2)] = calculate_xrel_abs(all_rawdata$facing_angle__rad[seq(1,nrow(all_rawdata),2)],
                                                                 all_rawdata$dist_to_other__mm[seq(1,nrow(all_rawdata),2)])


all_rawdata$rel_y_other[seq(2,nrow(all_rawdata),2)] = calculate_yrel(all_rawdata$facing_angle__rad[seq(2,nrow(all_rawdata),2)],
                                                         all_rawdata$dist_to_other__mm[seq(2,nrow(all_rawdata),2)])

all_rawdata$rel_x_other[seq(2,nrow(all_rawdata),2)] = calculate_xrel(ori = all_rawdata$ori__rad[seq(2,nrow(all_rawdata),2)],
                                                         xmale = all_rawdata$pos_x__px[seq(2,nrow(all_rawdata),2)],
                                                         xfemale = all_rawdata$pos_x__px[seq(1,nrow(all_rawdata),2)],
                                                         yrel = calculate_yrel(all_rawdata$facing_angle__rad[seq(2,nrow(all_rawdata),2)],
                                                                               all_rawdata$dist_to_other__mm[seq(2,nrow(all_rawdata),2)]))

all_rawdata$rel_x_abs_other[seq(2,nrow(all_rawdata),2)] = calculate_xrel_abs(all_rawdata$facing_angle__rad[seq(2,nrow(all_rawdata),2)],
                                                                 all_rawdata$dist_to_other__mm[seq(2,nrow(all_rawdata),2)])


all_rawdata$rel_x_abs_corr_other[which(all_rawdata$rel_x_other<0)] = -all_rawdata$rel_x_abs_other[which(all_rawdata$rel_x_other<0)]
all_rawdata$rel_x_abs_corr_other[which(all_rawdata$rel_x_other>0)] = all_rawdata$rel_x_abs_other[which(all_rawdata$rel_x_other>0)]

head(all_rawdata)
```



Using the copulation frames from the `all_genotypes` table we can subset the raw tracking data to remove all copulatory frames. We are then left with the non-copulatory frames.



```{r}
all_rawdata <- all_rawdata %>%
  unite("uni_fly",FileName,Id,remove = FALSE)

non_cop_frames <- tibble()
flies <- unique(all_genotypes$uni_fly)
for (fly in flies) {
  cop_time <- all_genotypes$copulation_time[all_genotypes$uni_fly==fly]
  cop_time <- replace_na(cop_time,900)
  cop_time <- cop_time*25
  temp0 <- all_rawdata %>%
    filter(uni_fly == fly) %>% 
    slice(1:cop_time)
  non_cop_frames <- bind_rows(non_cop_frames,temp0)
}
head(non_cop_frames)
```


Now we can join the genotype information from `all_genotypes` with the `non_cop_frames` table.


```{r}
non_cop_frames <- non_cop_frames %>%
  full_join(x = non_cop_frames, y = all_genotypes, by = c("uni_fly"="uni_fly")) %>% 
  select(-StartPosition) %>% 
  select(-copulation_time) %>% 
  select(-offset) %>% 
  select(-mp4_cop_time) %>% 
  select(-fly_id) %>% 
  select(-video) %>% 
  mutate(sex = if_else(genotype == "CS","male","female"))
head(non_cop_frames)
```


```{r}
fwrite(non_cop_frames, file = "non_copulatory_frames.csv",col.names = TRUE)
```


We calculate the the courtship per-frame courtship features from the JAABA annotations.

```{r}
non_cop_frames <- non_cop_frames %>%  
  group_by(uni_fly) %>% 
  mutate(
    Multitasking = (Approaching + Encircling + Contact + Turning + WingGesture),
    MultitaskingWithFacing = (Approaching + Encircling + Facing + Contact + Turning + WingGesture),
    Courtship = ifelse(Multitasking>=1, 1, 0),
    CourtshipWithFacing = ifelse(MultitaskingWithFacing>=1, 1, 0),
    MultitaskingWithCopulation = (Approaching + Encircling + Contact + Turning + WingGesture + Copulation),
    MultitaskingWithCopulationWithFacing = (Approaching + Encircling + Facing + Contact + Turning + WingGesture + Copulation),
    CourtshipAndCopulation = ifelse(MultitaskingWithCopulation>=1, 1, 0),
    CourtshipAndCopulationWthFacing = ifelse(MultitaskingWithCopulationWithFacing>=1, 1, 0),
    SmoothedCourtship = ifelse((rollmean(Courtship, 150, fill = c(0,0,0), align = c("left")))>0.5, 1, 0),
    SmoothedCopulation = ifelse((rollmean(Copulation, 1250, fill = c(0,0,0), align = c("center")))>0.5, 1, 0)
  )
head(non_cop_frames)
```


```{r}
fwrite(non_cop_frames, file = "non_copulatory_frames_with_summary_features.csv",col.names = TRUE)
```

Just double checking our column names.

```{r}
colnames(non_cop_frames)
```


Based on the per-frame courtship features we can now calculate the courtship initiation using the first instance of the `SmoothedCourthsip` parameter.


```{r}
start_of_courtship_frames <- non_cop_frames %>% 
  filter(sex != "female") %>% 
  summarise(FileName = unique(FileName),
            Arena = unique(Arena),
            Id = unique(Id),
            genotype = unique(genotype),
            treatment = unique(treatment),
            start_of_courtship = which.max(SmoothedCourtship))
head(start_of_courtship_frames)
```





As with the `all_genotypes` table, we doublicate the `start_of_courtship` table to get the corresponding values for the females.

```{r}
female_start_of_courtship_frames <- start_of_courtship_frames
even_ids <- (start_of_courtship_frames$Id %% 2) == 0
odd_ids <- (start_of_courtship_frames$Id %% 2) != 0
female_start_of_courtship_frames$Id[even_ids] = female_start_of_courtship_frames$Id[even_ids] - 1
female_start_of_courtship_frames$Id[odd_ids] = female_start_of_courtship_frames$Id[odd_ids] + 1
female_start_of_courtship_frames$genotype <- female_start_of_courtship_frames$treatment
head(female_start_of_courtship_frames)
```



And then merge them together.


```{r}
all_start_of_courtship_frames <- bind_rows(start_of_courtship_frames,female_start_of_courtship_frames)
all_start_of_courtship_frames <- all_start_of_courtship_frames %>% 
  ungroup() %>% 
  select(-uni_fly) %>% 
  unite("uni_fly", FileName, Id, remove = FALSE) %>% 
  group_by(uni_fly)
head(all_start_of_courtship_frames)
```




Now we can subset the `non_cop_frames` to remove the frames before courtship was initiated.


```{r}
courting_frames <- tibble()
flies <- unique(all_start_of_courtship_frames$uni_fly)
for (fly in flies) {
  court_time <- all_start_of_courtship_frames$start_of_courtship[all_start_of_courtship_frames$uni_fly==fly]
  temp0 <- non_cop_frames %>% filter(uni_fly == fly)
  temp0 <- temp0 %>% slice(court_time:n())
  courting_frames <- bind_rows(courting_frames,temp0)
}
head(courting_frames)
```

And we can calculate a few ipsi- v contra-lateral wing features.

```{r}
courting_frames <- courting_frames %>% 
  mutate(ipsi_wing_ang = if_else(rel_x_abs_corr_other>0,
                                 wing_r_ang__rad,
                                 -wing_l_ang__rad),
         contra_wing_ang = if_else(rel_x_abs_corr_other<0,
                                 -wing_r_ang__rad,
                                 wing_l_ang__rad)
         )
head(courting_frames)
```



```{r}
courting_frames <- courting_frames %>% 
  mutate(ipsi_contra_rel_x = if_else(ipsi_wing_ang >= abs(contra_wing_ang),
                                 abs(rel_x_abs_corr_other),
                                 -abs(rel_x_abs_corr_other))
         )
head(courting_frames)
```





Save the data.

```{r}
fwrite(courting_frames, file = "courting_frames_with_summary_features.csv",col.names = TRUE)
```





# **The Plots**


And finally we can start plotting the data.

First "port of call" is of course Courtship Index. And there isn't much of a visual difference.

(the stats will follow, but first lets plot the data)

And just a reminder of the genotypes:

a = _Otd-FLP/+; dsx[Gal4.DBD]/+_ (n=29) 

b = _VGlut[dVP16.AD], UAS>stop>TNT/+_ (n=19)

c = _VGlut[dVP16.AD], UAS>stop>TNT/+; dsx[Gal4.DBD]/+_ (n=41)

d = _VGlut[dVP16.AD], UAS>stop>TNT/Otd-FLP; dsx[Gal4.DBD]/+_ (n=46)



```{r warning=F,message=F,fig.width=4,fig.height=4}
indices <- courting_frames %>%
  filter(sex != "female") %>% 
  group_by(uni_fly) %>% 
  summarise(genotype = unique(treatment),
            CI = 100*sum(Courtship)/length(Frame),
            CIwF = 100*sum(CourtshipWithFacing)/length(Frame),
            approaching = 100*sum(Approaching)/length(Frame),
            contact = 100*sum(Contact)/length(Frame),
            circling = 100*sum(Encircling)/length(Frame),
            facing = 100*sum(Facing)/length(Frame),
            turning = 100*sum(Turning)/length(Frame),
            wing = 100*sum(WingGesture)/length(Frame)
            ) 

indices %>% 
    ggplot(aes(x=genotype,y=CIwF)) +
    geom_boxplot(outlier.size = 0) +
    geom_beeswarm(shape = 21, colour = "black", fill = "white", size = 2, stroke = 1) +
    ylim(0,100) +
    ylab("Courtship Index (%)") + 
    xlab("Genotype")
```


We can look at the individual courtship features to see what they look like. But as with CI, there doesn't look like there is any effect.

```{r warning=F,message=F,fig.width=12,fig.height=8}
p <- list()
courtship_features <- c("approaching","facing","contact","circling","turning","wing")
for (i in 1:length(courtship_features)) {
    p[[i]] <- indices %>% 
        ggplot(aes_string(x="genotype",y=courtship_features[i])) +
        geom_boxplot(outlier.size = 0) +
        geom_beeswarm(shape = 21, colour = "black", fill = "white", size = 2, stroke = 1) +
        #geom_quasirandom(method = "smiley",shape = 21, colour = "black", fill = "white", size = 2, stroke = 1) +
        ylim(0,100) +
        ylab(as.name(courtship_features[i])) + 
        xlab("Genotype")
}
plot_grid(plotlist = p,ncol = 3)
```




There also doesn't look like much of an effect on courtship initiation.


```{r warning=F,message=F,fig.width=4,fig.height=4}
ggplot(start_of_courtship_frames,aes(x=treatment,y=start_of_courtship/1500)) +
    geom_boxplot() +
    ylim(0,10) +
    geom_boxplot(outlier.size = 0) +
    geom_beeswarm(shape = 21, colour = "black", fill = "white", size = 2, stroke = 1) +
    ylab("Courtship Initiation (min.)") + 
    xlab("Genotype")
```


There also doesn't look like much of an effect on cumulative copulation.

```{r fig.height=4, fig.width=6, message=F,warning=F}
df <- genotypes %>% 
  mutate(status = if_else(is.na(copulation_time),0,1))
df$copulation_time <- replace_na(df$copulation_time,3600)
df$copulation_time <- round(as.numeric(df$copulation_time)/60)
fit <- survfit(Surv(copulation_time, status) ~ treatment, data = df)
ggsurv <- ggsurvplot(
            fit,        
            data = df,
            risk.table = TRUE, 
            pval = FALSE, 
            conf.int = TRUE, 
            xlim = c(0,60),   
            xlab = "Time in minutes", 
            break.time.by = 10, 
            risk.table.y.text.col = T,
            risk.table.height = 0.25, 
            risk.table.y.text = FALSE,
            ncensor.plot = TRUE, 
            ncensor.plot.height = 0.25,
            fun = "event"
        )
ggsurv$plot 
```


Looking at the position of the female while the male has it's wing extended, also looks quite similar. Which is in contrast to the male aDN experiments. (_NB_: contralateral = left, ipsilateral = right, and the males postion is the centre)


```{r warning=F,message=F,fig.width=16,fig.height=4}
p <- list()
treatment <- c("a","b","c","d")
for (i in 1:length(treatment)) {
    p[[i]] <- courting_frames %>% 
                  filter(sex == "male") %>% 
                  filter(treatment==treatment[i]) %>%
                  filter(max_wing_ang__rad > (35*pi/180)) %>%
                  ggplot(aes(x=ipsi_contra_rel_x,y=rel_y_other)) +
                  geom_bin2d(bins = c(400,400)) +
                  xlim(-20,20) +
                  ylim(-20,20) + 
                  scale_fill_continuous(limits = c(0,400),na.value = "white") +
                  theme_void() +
                  coord_fixed() +
                  ggtitle(treatment[i])
}
plot_grid(plotlist = p,ncol = 4)
```




Here we write a little function to look at the probability density plots of a given feature with a mean trend line and 95% confidence intervals.


```{r}
mean_pd <- function(input,feature,low=0,high,wing=TRUE,wing_ang=NULL, n=512){
  input <- input %>%
    filter(sex != "female") %>% 
    select(uni_fly,Frame,genotype,treatment,sex,feature, max_wing_ang__rad)
  
  output <- tibble()
  flies <- unique(input$uni_fly)
  for (fly in flies) {
    temp0 <- input %>%
      filter(uni_fly == fly) %>% 
      do(
        if(wing)
          filter(., max_wing_ang__rad > wing_ang)
        else
          .
      )
    #message(dim(temp0)[1])
    if(dim(temp0)[1]<100) next
    
    feat <- temp0[[feature]][!is.na(temp0[[feature]])]
    den <- density(feat, from = low, to = high, n = n, na.rm = TRUE)
    temp1 <- tibble()
    temp1 <- tibble(uni_fly = rep(unique(temp0$uni_fly),length(den[["x"]])),
                    sex = rep(unique(temp0$sex),length(den[["x"]])),
                    genotype = rep(unique(temp0$genotype),length(den[["x"]])),
                    treatment = rep(unique(temp0$treatment),length(den[["x"]])),
                    x = den[["x"]],
                    pd = den[["y"]])
    output <- bind_rows(output,temp1)
  }
  return(output)
}
```




And there isn't anything strikingly different in the density of facing angle.


```{r warning=F,message=F,fig.width=6,fig.height=4}
facing_den <- mean_pd(input = courting_frames,feature = "facing_angle__rad",low = 0,high = pi, wing = FALSE, n=50)
facing_den %>%
  filter(sex == "male") %>%
  group_by(treatment,x) %>% 
  summarise(y = mean(pd),
            err = qt(0.95,df=length(pd)-1)*sd(pd)/sqrt(length(pd))) %>% 
  ggplot(aes(x=x*180/pi, y=100*y*pi/180)) +
  geom_line(aes(colour=treatment), size=1) +
  geom_ribbon(aes(ymin=if_else(y-err<0,0,(y-err)*100*pi/180), ymax=(y+err)*100*pi/180, fill=genotype), alpha = 0.3) +
  ylab("Density (%/deg.)") +
  xlab("Facing angle (deg.)") +
  ylim(0,6) +
  xlim(0,180)
```


Or distance.

```{r warning=F,message=F,fig.width=6,fig.height=4}
distance_den <- mean_pd(input = courting_frames,feature = "dist_to_other__mm",low = 0,high = 20, wing = FALSE, n=50)
distance_den %>%
  filter(sex == "male") %>%
  group_by(treatment,x) %>% 
  summarise(y = mean(pd),
            err = qt(0.95,df=length(pd)-1)*sd(pd)/sqrt(length(pd))) %>% 
  ggplot(aes(x=x, y=y*100)) +
  geom_line(aes(colour=treatment), size=1) +
  geom_ribbon(aes(ymin=if_else(y-err<0,0,(y-err)*100), ymax=(y+err)*100, fill=genotype), alpha = 0.3) +
  ylab("Density (%/mm)") +
  xlab("Distance to other (mm)") +
  ylim(0,60) +
  xlim(0,20) 
```




When we quantify the mean facing angle, mean distance to other, and minimum distance to other there is no difference between the flies. 


```{r warning=F,message=F,fig.width=12,fig.height=4}
p <- list()
p[[1]] <- courting_frames %>% 
  filter(sex != "female") %>% 
  group_by(uni_fly) %>%  
  summarise(genotype = unique(treatment),
            facing = mean(facing_angle__rad)
  ) %>% 
  ggplot(aes(x=genotype,y=facing*180/pi)) +
  geom_boxplot() +
  geom_beeswarm(shape = 21, colour = "black", fill = "white", size = 2, stroke = 1) +
  ylab("Mean Facing Angle (deg.)") +
  ylim(0,180)
p[[2]] <- courting_frames %>% 
  filter(sex != "female") %>%
  group_by(uni_fly) %>% 
  summarise(mean_dist = mean(dist_to_other__mm),
            genotype = unique(treatment)) %>% 
  ggplot(aes(x=genotype, y=mean_dist)) +
  geom_boxplot() +
  geom_beeswarm(shape = 21, colour = "black", fill = "white", size = 2, stroke = 1) +
  ylab("Mean Distance to Other (mm)") +
  ylim(0,15) 
p[[3]] <- courting_frames %>% 
  filter(sex != "female") %>% 
  group_by(uni_fly) %>% 
  summarise(min_dist = min(dist_to_other__mm),
            genotype = unique(treatment)) %>% 
  ggplot(aes(x=genotype, y=min_dist)) +
  geom_boxplot() +
  geom_beeswarm(shape = 21, colour = "black", fill = "white", size = 2, stroke = 1) +
  ylab("Min. Distance to Other (mm)") +
  ylim(0,3) 
p[[4]] <- courting_frames %>% 
  filter(sex != "female") %>% 
  group_by(genotype) %>% 
  group_by(uni_fly) %>% 
  summarise(genotype = unique(treatment),
            both_wing_index = 100*sum(min_wing_ang__rad>(15*pi/180), na.rm = TRUE)/
              length(Frame)
  ) %>% 
  ggplot(aes(x=genotype, y=both_wing_index)) +
  geom_boxplot() +
  geom_beeswarm(shape = 21, colour = "black", fill = "white", size = 2, stroke = 1) +
  ylab("Bilateral wing index (%)") +
  ylim(0,100) 
plot_grid(plotlist = p,ncol = 4)
```




There is no apparent difference in wing choice index ether.


```{r warning=F,message=F,fig.width=4,fig.height=4}
courting_frames %>% 
  filter(sex != "female") %>% 
  group_by(uni_fly) %>% 
  summarise(genotype = unique(treatment),
            wing_choice = (sum(abs(ipsi_wing_ang)>(35*pi/180),na.rm = T)-sum(abs(contra_wing_ang)>(35*pi/180),na.rm = T))/
              (sum(abs(ipsi_wing_ang)>(35*pi/180),na.rm = T)+sum(abs(contra_wing_ang)>(35*pi/180),na.rm = T))
  ) %>% 
  ggplot(aes(x=genotype,y=wing_choice)) +
  geom_boxplot() +
  geom_beeswarm(shape = 21, colour = "black", fill = "white", size = 2, stroke = 1) +
  ylab("Wing Choice Index") +
  ylim(-1,1)
```








# **The Stats**



First lets compute a summary table of the features.


```{r}
court_summary <- courting_frames %>% 
  filter(sex!="female") %>% 
  group_by(uni_fly) %>% 
  summarise(genotype = unique(treatment),
            initiation = min(Frame),
            CI = 100*sum(CourtshipWithFacing)/length(Frame),
            approaching = 100*sum(Approaching)/length(Frame),
            contact = 100*sum(Contact)/length(Frame),
            circling = 100*sum(Encircling)/length(Frame),
            facing = 100*sum(Facing)/length(Frame),
            turning = 100*sum(Turning)/length(Frame),
            wing = 100*sum(WingGesture)/length(Frame),
            time_behind = 100*sum(facing_angle__rad > (25*pi/180))/length(Frame),
            mean_facing_angle = mean(facing_angle__rad),
            mean_dist = mean(dist_to_other__mm),
            min_dist = min(dist_to_other__mm),
            bilateral_wing_index = 100*sum(min_wing_ang__rad>(15*pi/180), na.rm = TRUE)/length(Frame),
            uni_wing_index = 100*sum((max_wing_ang__rad>(35*pi/180) & min_wing_ang__rad < (15*pi/180)), na.rm = TRUE)/length(Frame),
            wing_choice = (sum(abs(ipsi_wing_ang)>(35*pi/180),na.rm = T)-sum(abs(contra_wing_ang)>(35*pi/180),na.rm = T))/
              (sum(abs(ipsi_wing_ang)>(35*pi/180),na.rm = T)+sum(abs(contra_wing_ang)>(35*pi/180),na.rm = T)),
            mean_min_wing = mean(min_wing_ang__rad)*180/pi
            )


temp <- courting_frames %>% 
  filter(sex == "male")
uniq_fly <- unique(temp$uni_fly)
bi_wing_bouts <- tibble()
for (fly in uniq_fly) {
  temp2 <- temp %>% 
    filter(uni_fly == fly) %>%
    mutate(bin_bilateral_wing = if_else(min_wing_ang__rad>(15*pi/180),1,0)
         )
  temp2$bin_bilateral_wing <- temp2$bin_bilateral_wing %>% replace_na(0)
  bilateral_wing_bouts <- rle(temp2[["bin_bilateral_wing"]])
  temp3 <- tibble(uni_fly = fly,
                  genotype = unique(temp2[["treatment"]]),
                  bilateral_wing_bout_rate = 60*25*sum(bilateral_wing_bouts$values==1)/length(temp2[["Frame"]]),
                  bilateral_wing_bout_length = mean(bilateral_wing_bouts$lengths[bilateral_wing_bouts$values==1])/25
                  )
  bi_wing_bouts <- bind_rows(bi_wing_bouts,temp3)
}
court_summary <- left_join(court_summary,bi_wing_bouts)
head(court_summary)
```





And now we calculate a stats table and adjust for multiple comparisons/testing. Although not all the features were plotted above and calculating the stats for all the corresponding figures that we show for the in light experiments.


```{r}
features <- c("initiation","CI","mean_facing_angle","mean_dist","min_dist","bilateral_wing_index","bilateral_wing_bout_rate",
              "approaching","facing","contact","circling","turning","wing",
              "time_behind","uni_wing_index","bilateral_wing_bout_length","wing_choice")
figures <- c("4a","4b","4g","4h","4i","4j","4k",
             "s4a","s4b","s4c","s4d","s4e","s4f",
             "s4g","s4h","s4i","s4j")
all_pvals <- tibble()
anova_values <- tibble()
for (ii in 1:length(features)) {
  aov <- aov(court_summary[[features[ii]]]~court_summary[["genotype"]])
  temp_anova <- tibble(figure = figures[ii],
                       feature = features[ii],
                       df1 = summary(aov)[[1]][["Df"]][1],
                       df2 = summary(aov)[[1]][["Df"]][2],
                       fvalue = summary(aov)[[1]][["F value"]][1]
                    )
  anova_values <- bind_rows(anova_values,temp_anova)
  if (summary(aov)[[1]][["Pr(>F)"]][[1]]<0.05) {
    d_a <- t.test(court_summary[[features[ii]]][court_summary$genotype=="d"],court_summary[[features[ii]]][court_summary$genotype=="a"])
    d_b <- t.test(court_summary[[features[ii]]][court_summary$genotype=="d"],court_summary[[features[ii]]][court_summary$genotype=="b"])
    d_c <- t.test(court_summary[[features[ii]]][court_summary$genotype=="d"],court_summary[[features[ii]]][court_summary$genotype=="c"])
    temp_pvals <- tibble(figure = figures[ii],
                        feature = features[ii],
                        comparison = c("anova", "d-a t.test", "d-b t.test", "d-c t.test"),
                        pvals = c(summary(aov)[[1]][["Pr(>F)"]][[1]],d_a$p.value,d_b$p.value,d_c$p.value)
                    )
    all_pvals <- bind_rows(all_pvals,temp_pvals)
  } else {
      d_a <- NA
      d_b <- NA
      d_c <- NA
      temp_pvals <- tibble(figure = figures[ii],
                          feature = features[ii],
                          comparison = c("anova", "d-a t.test", "d-b t.test", "d-c t.test"),
                          pvals = c(summary(aov)[[1]][["Pr(>F)"]][[1]],NA,NA,NA)
                      )
      all_pvals <- bind_rows(all_pvals,temp_pvals)
  }
}

res0 <- survdiff(formula = Surv(copulation_time, status) ~ treatment, data = df)
res <- pairwise_survdiff(formula = Surv(copulation_time, status) ~ treatment, data = df, p.adjust.method = "none")
temp_pvals <- tibble(figure = "4c",
                     feature = "copulation",
                     comparison = c("chisq", "d-a log-rank test", "d-b log-rank test", "d-c log-rank test"),
                     pvals = c(1 - pchisq(res0$chisq, length(res0$n) - 1),res[["p.value"]][3,1],res[["p.value"]][3,2],res[["p.value"]][3,3])
                      )
all_pvals <- bind_rows(all_pvals,temp_pvals)

a_pd <- distance_den %>% filter(treatment == "a") %>% group_by(x) %>% summarise(y = mean(pd))
b_pd <- distance_den %>% filter(treatment == "b") %>% group_by(x) %>% summarise(y = mean(pd))
c_pd <- distance_den %>% filter(treatment == "c") %>% group_by(x) %>% summarise(y = mean(pd))
d_pd <- distance_den %>% filter(treatment == "d") %>% group_by(x) %>% summarise(y = mean(pd))
d_a <- ks.test(d_pd$y, a_pd$y, exact = TRUE)
d_b <- ks.test(d_pd$y, b_pd$y, exact = TRUE)
d_c <- ks.test(d_pd$y, c_pd$y, exact = TRUE)

temp_pvals <- tibble(figure = "4e",
                     feature = "dist_to_other",
                     comparison = c("d-a ks test", "d-b ks test", "d-c ks test"),
                     pvals = c(d_a$p.value,d_b$p.value,d_c$p.value)
                    )
all_pvals <- bind_rows(all_pvals,temp_pvals)

a_pd <- facing_den %>% filter(treatment == "a") %>% group_by(x) %>% summarise(y = mean(pd))
b_pd <- facing_den %>% filter(treatment == "b") %>% group_by(x) %>% summarise(y = mean(pd))
c_pd <- facing_den %>% filter(treatment == "c") %>% group_by(x) %>% summarise(y = mean(pd))
d_pd <- facing_den %>% filter(treatment == "d") %>% group_by(x) %>% summarise(y = mean(pd))
d_a <- ks.test(d_pd$y, a_pd$y, exact = TRUE)
d_b <- ks.test(d_pd$y, b_pd$y, exact = TRUE)
d_c <- ks.test(d_pd$y, c_pd$y, exact = TRUE)

temp_pvals <- tibble(figure = "4d",
                     feature = "facing_angle",
                     comparison = c("d-a ks test", "d-b ks test", "d-c ks test"),
                     pvals = c(d_a$p.value,d_b$p.value,d_c$p.value)
                    )
all_pvals <- bind_rows(all_pvals,temp_pvals)

all_pvals <- all_pvals %>% 
  mutate(p_adj = p.adjust(pvals,"holm"),
         #sig = ifelse(p_adj<0.05,"y","n"),
         sig_level = ifelse(p_adj>0.1,"ns",
                            ifelse(p_adj>0.05,".",
                                    ifelse(p_adj>0.01,"*",
                                            ifelse(p_adj>0.001,"**",
                                                    ifelse(p_adj>0.001,"***","****")
                                                   )
                                           )
                                    )
                            )
         )
all_pvals <- all_pvals %>% arrange(figure) 
all_pvals
```










# **Session info**

```{r session_info}
sessionInfo()
```





























































































